Introducing SCM to a small company

### 2012-01-11 article.tex

\end{abstract}

@@

\subsection{Generally}
The identification part of the plan contains useful information about how objects should be treated. One must decide whether or not the object should be under version control. When this should be decided one should ask the question “Is it necessary to have this object under version control in order to be able to build the complete, working release?”. If the answer to that question is yes, then the object should be configuration item (an item under version control).
Usually, the major part of the object should be under version control. What usually shouldn't be under version control is items such as PM, mails, announcements, memos.

@@

\subsection{Particularly}
Since we will be implementing the SCM plan iteratively we will start off with some baselines.

@@

-source code

@@

\section{Configuration Status Accounting}

\section{Configuration Auditing}

>>>>

\end{abstract}
\newpage

\tableofcontents
\newpage

@@

\subsection{Background}
The identification part of the plan contains useful information about how objects should be treated. One must decide whether or not the object should be under version control. When this should be decided one should ask the question “Is it necessary to have this object under version control in order to be able to build the complete, working release?”. If the answer to that question is yes, then the object should be configuration item (an item under version control).
Usually, the major part of the object should be under version control. What usually shouldn't be under version control is items such as PM, mails, announcements, memos.

@@

\subsection{This software}

Kanske lite diagram visande CI

Binären måste kontrolleras, dokumentation i versionskontroll också
Design dokument, diagram måste numreras/hanteras

Since we will be implementing the SCM plan iteratively we will start off with some baselines.

@@

-source code
Levereras som binär + dokumentation.
Mjukvara har inbyggd ``labelling''

\subsection{Version control}
Med lämplig mjukvara för kod + dokumentation.
Design dokument binära och hanterasw av icke-kodare (akm) bättre med central filserver+versionsnummer manuellt.

@@

Hur stor ccb?
Hur rigorös CR kontroll?

\subsection{Branching Pattern}

Hitt' på nåt.
Hur vill vi det ska fungera (utan att ta hänsyn till verktyg här, ta det senare)
